Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
improvements examples

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\subsection{Faces of the type-cone and Minkowski sums}
Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.

@@

We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda\geq 0$ and a polytope~$Q$ such that $\lambda R=P+Q$. 
\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes. Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by Meyer in~\cite{Meyer1974}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).

This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone. These correspond to indecomposable polytopes~(cf.~\cite{Meyer1974} or \cite{McMullen-typeCone}). A polytope $P$ in $\R^n$ is 
  called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda\geq 0$ and $t\in\R^n$.

\begin{corollary}
\arnau{See \cite{Meyer1974} and \cite{McMullen-typeCone}}
Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
\end{corollary}

If $P=Q+R$, then we say that $R$ is the \defn{Minkowski difference} of $P$ and $Q$, which we denote by $R=P-Q$. We will only consider the case where $Q$ is a summand of $P$.
There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P-Q=\set{x\in\R^n}{x+Q\subseteq P}$. 
Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$. Considering arbitrary differences of support functions gives rise to  \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii1992}.

\begin{corollary}
Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$. Then every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
\end{corollary}
\begin{proof}
 It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
\end{proof}

This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquelyas a signed Minkowski sum of simplices. 
\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
In the particular case when the type-cone is simplicial, then we can get rid of the Minkowski differences.
\begin{corollary}
 If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$
 verify that 
 \begin{enumerate}[(i)]
  \item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
 \item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
 \end{enumerate}

\end{corollary}
 Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.

@@

\begin{example}
\label{exm:typeConeGA}
Consider the nested fans illustrated in \cref{fig:nestedFans}.
The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below). In particular, it is not simplicial.

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 
\text{space}		& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 
\text{space}		& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

\vincent{Todo}
\end{example}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic, nicefrac}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\subsection{Faces of the type-cone}

\subsection{Minkowski sums}

Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.

@@

We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${\lambda R = P + Q}$. 
\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes. Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).

This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone. These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}. A polytope $P$ in $\R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.

\begin{corollary}
\arnau{See \cite{Meyer} and \cite{McMullen-typeCone}}
Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
\end{corollary}

If $P = Q + R$, then we say that~$R$ is the \defn{Minkowski difference} of~$P$ and~$Q$, denoted~${R = P - Q}$. Note that this is only defined when~$Q$ is a Minkowski summand of~$P$.
There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P - Q = \set{x \in \R^n}{x + Q \subseteq P}$. 
Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$. Considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.

\begin{corollary}
Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$. Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
\end{corollary}
\begin{proof}
 It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
\end{proof}

This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquely as a signed Minkowski sum of simplices. 
\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
In the particular case when the type-cone is simplicial, then we can get rid of the Minkowski differences.

\begin{corollary}
If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
\begin{enumerate}[(i)]
\item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
\end{enumerate} 
\end{corollary}

Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.

@@

\begin{example}
\label{exm:typeConeGA}
Consider the nested fans illustrated in \cref{fig:nestedFans}.
The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $19$ facet defining inequalities (given below). In particular, it is not simplicial.

\[
\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{0}{2}{-1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]

\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
\text{space}		& -2 & -1 & 0 & -2 & 0 & 0 & -4 & 0 & 4 & 2 & 2 & 1 & 0 \\
					& 0 & 0 & -1 & 1 & -2 & 0 & 2 & 0 & -2 & 0 & -1 & 0 & 1 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -2 & 0 \\
					& -1 & 2 & 0 & -1 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 & 2 & -1 \\
					& -1 & 2 & -1 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& -1 & 0 & 0 & 0 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & 0 & 2 & 0 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 2 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & 0 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 \\
					& 1 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & 0 & 0 & 0 & -1 & 0 & 1 & 0 & 0 & -1 \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & -2 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
\end{array}
\]

%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[1,4],[2,3],[3,4]]])
%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
%sage: rays
%{(1,): (1, 0, 0),
% (1, 2): (0, 1, 0),
% (1, 2, 3): (0, 0, 1),
% (1, 2, 3, 4): (0, 0, 0),
% (1, 2, 4): (0, 2, -1),
% (1, 3): (1/2, -1, 1/2),
% (1, 3, 4): (1, -2, 0),
% (1, 4): (1/2, 0, -1/2),
% (2,): (-1, 2, 0),
% (2, 3): (-1/2, 0, 1/2),
% (2, 3, 4): (-1, 0, 0),
% (3,): (0, -2, 1),
% (3, 4): (0, -1, 0),
% (4,): (0, 0, -1)}

%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
%sage: NF.rays()
%N( 0, -1,  0),
%N( 0,  2, -1),
%N( 1,  0,  0),
%N(-1,  2,  0),
%N( 0,  0,  1),
%N( 1, -2,  0),
%N( 0, -2,  1),
%N( 0,  0, -1),
%N(-1,  0,  1),
%N( 1,  0, -1),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 1, -2,  1)
%in 3-d lattice N

%sage: TCNF = type_cone(NF)
%sage: TCNF
%A 13-dimensional polyhedron in QQ^13 defined as the convex hull of 1 vertex, 25 rays, 3 lines
%sage: TCNF.lines()
%(A line in the direction (0, 0, 1, -1, 0, 1, 0, 0, -1, 1, -1, 0, 1),
% A line in the direction (1, -2, -2, 0, 0, 0, 2, 0, 2, -2, 2, -1, 0),
% A line in the direction (0, 1, 0, 0, -1, 0, -1, 1, -1, 1, 0, 0, -1))
%sage: TCNF.inequalities()
%(An inequality (-2, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (-2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, -1, -1, 0, 0, 0, 0, 0, 0, 1, 0, 2, 0) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, 0, -1, 0, 1, 0, -1, 0, 0) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 0, -1, 0, 0, 0, 0, 0, 0, 2, 1) x + 0 >= 0,
% An inequality (0, 0, -1, 0, 0, -1, 0, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 0, 0, -1, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, -1, -1, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 1, 0, -1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
% An inequality (0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
% An inequality (0, 1, 0, -1, 0, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 1, 0, 0, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0)
%sage: len(TCNF.inequalities())
%12

\noindent
The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $12$ facet defining inequalities (given below). In particular, it is not simplicial.

\[
\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\
\text{space}		& 1 & 0 & 0 & 2 & 1 & -1 & -2 & -1 & 0 & 0 & 0 \\
					& 1 & 0 & 1 & 4 & 1 & -1 & 0 & -1 & 1 & 0 & -1 \\[.2cm]
\text{inequalities} & -1 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 1 & -2 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 2 & -1 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 \\
					& 1 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
					& 0 & 0 & -1 & 2 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & -1 & 2 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -2 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
\end{array}
\]

%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[2,3],[3,4]]])
%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
%sage: rays
%{(1,): (1, 0, 0),
% (1, 2): (0, 1, 0),
% (1, 2, 3): (0, 0, 1),
% (1, 2, 3, 4): (0, 0, 0),
% (1, 3): (1/2, -1, 1/2),
% (1, 3, 4): (1, -2, 0),
% (2,): (-1, 2, 0),
% (2, 3): (-1/2, 0, 1/2),
% (2, 3, 4): (-1, 0, 0),
% (3,): (0, -2, 1),
% (3, 4): (0, -1, 0),
% (4,): (0, 0, -1)}

%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
%sage: NF.rays()
%N( 1,  0,  0),
%N(-1,  2,  0),
%N( 0,  0,  1),
%N( 1, -2,  0),
%N( 0,  0, -1),
%N(-1,  0,  1),
%N( 1, -2,  1),
%N( 0, -2,  1),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0, -1,  0)
%in 3-d lattice N

%sage: TCNF = type_cone(NF)
%sage: TCNF
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 11 rays, 3 lines
%sage: TCNF.lines()
%(A line in the direction (0, 2, 0, -2, 0, 0, -2, -2, 0, 1, -1),
% A line in the direction (1, -1, 0, 1, 0, -1, 1, 0, -1, 0, 0),
% A line in the direction (1, -1, 1, 1, -1, 0, 2, 1, -1, 0, 0))
%sage: TCNF.inequalities()
%(An inequality (-1, 0, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
% An inequality (0, -1, -1, 0, 0, 1, 0, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 0, 0, 1, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, -1, 0, 0, 1, -1, 0, 0, 2) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, -1, -1, 0, 2) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, 0, 1, 0, 0, -2) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 0, 0, 1, 0, -2) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 1, 0, 0, -1, 0, 0, 0, 0) x + 0 >= 0)
%sage: len(TCNF.inequalities())
%12
\end{example}
